Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Add section text to "Implementation"

\item[property]
    A property is something that is testable with
    QuickCheck~\cite{quickcheck}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Implementation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Haddock}
\label{sec:haddock}

@@

We showed how to apply behavior driven development to
Haskell.  We proposed to use Doctest for user documentation and Hspec
for code documentation. We extended Haddock's markup with support for
examples and properties.  And we implemented Doctest, which verifies
examples and tests properties in Haddock comments.
We added two missing features to Hspec: Combinators to express
expectations, and a mechanism for automatic discovery of specs.
And we showed how to reuse pieces of specification.
Our approach can be used for design, documentation and automated
testing.  We hope that this motivates Haskell programmers to write
more and better tests.

>>>>

\item[property]
    A property is something testable with
    QuickCheck~\cite{quickcheck}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Implementation}

In this section we describe implementation aspects of the proposed
solution.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Haddock}
\label{sec:haddock}

@@

We showed how to apply behavior driven development to
Haskell.  We proposed to use Doctest for user documentation and Hspec
for code documentation. We extended Haddock's markup with support for
examples and properties.  And we implemented Doctest, which verifies
examples and tests properties in Haddock comments.
We added two missing features to Hspec: combinators to express
expectations, and a mechanism for automatic discovery of specs.
And we showed how to reuse pieces of specification.
Our approach can be used for design, documentation and automated
testing.  We hope that this motivates Haskell programmers to write
more and better tests.
